Simulating High-Dimensional Multivariate Data using the bigsimr R Package

### 2020-10-21 030-bigsimr-package.Rmd

```{r setup3, eval = TRUE}
## setwd('~/Research/article_bigsimr/'); bookdown::preview_chapter('030-bigsimr-package.Rmd')
## bookdown::render_book('index.html')
library(bigsimr)
library(reticulate)
reticulate::use_condaenv("bigsimr-cpu")
```

@@

```{r setMargins}
margins = alist(
  qnorm(mean = 3.14, sd = 0.1),
  qbeta(shape1 = 1, shape2 = 4),
  qnbinom(size = 10, prob = 0.75)
)
```

@@

```{r setCor}
rho <- matrix(0.5, nrow = 3, ncol = 3)
diag(rho) <- 1.0
rho
```

@@

```{r rvec10}
x <- bigsimr::rvec(10, rho = rho, margins = margins, type = "spearman")
```

```{r gpuWarn, echo=FALSE}
warning("warning.warn('No GPU/TPU found, falling back to CPU.')")
```

@@

```{r printX}
x
```

@@

```{r rvec1e6, fig.width=7}
x <- rvec(1e6, rho = rho, margins = margins, type = "spearman")

@@

```{r fastCor}
bigsimr::fastCor(x, method = 'spearman')
```

@@

```{r computeBounds, echo = TRUE, eval=FALSE}
## Possibly bug? or configuration
## Error: segfault from C stack overflow on my Okapi bigsimr env 
rho_bounds <- bigsimr::computeCorBounds(margins = margins, type = 'spearman', cores = 1, reps = 1e5)
rho_bounds
```

@@

```{r rvecRslurm, echo=TRUE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)
```

```{r rvecRslurmRes, echo=TRUE, eval=FALSE}
res <- readRDS(file.path('_rslurm_rvec', list.files('_rslurm_rvec', 'results')))
head(res, 3)
## cleanup_files(sjob) ## careful this deletes output also
```

@@

```{r rvecRslurmMap, echo=TRUE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
set.seed(06202020)
simReps <- 100
rhoList <- replicate( n = simReps, bigsimr::rcor(d = length(margins), constant_rho = TRUE), simplify=FALSE )
sjob <- slurm_map(x = rhoList,
                  f = rvec,
                  jobname = 'rvecMap',
                  n=1e6,
                  margins = margins,
                  type = "spearman",
                  nodes = 4,
                  cpus_per_node = 4,
                  submit = TRUE)

@@

```{r rvecRslurmMapRes, echo=TRUE, eval=FALSE}
list.files('_rslurm_rvecMap', 'results')
res <- rslurm::get_slurm_out(sjob, outtype = 'raw')
rhoHats <- lapply( res, bigsimr::fastCor, method = 'spearman' )

@@

```{r rvecRslurmMapFig, echo = TRUE, eval=TRUE, message=FALSE, warning=FALSE, out.width= '75%', fig.align='center', fig.cap='The continous marginal pairs exact reproduce the specified correlation whereas the discrete pairs (green nad blue) show a downward bias. Future work with employ a discrete adjusted procedures using *rescaling* on the traditional correlation coefficient.'}
library(tidyverse)

>>>>

```{r ch030-setup, eval = FALSE}
## setwd('~/Research/article_bigsimr/'); bookdown::preview_chapter('030-bigsimr-package.Rmd')
## bookdown::render_book('index.html')
library(bigsimr)
library(reticulate)
reticulate::use_condaenv("bigsimr-cpu")
```

@@

```{r ch030-setMargins, eval = FALSE}
margins = alist(
  qnorm(mean = 3.14, sd = 0.1),
  qbeta(shape1 = 1, shape2 = 4),
  qnbinom(size = 10, prob = 0.75)
)
```

@@

```{r ch030-setCor, eval = FALSE}
rho <- matrix(0.5, nrow = 3, ncol = 3)
diag(rho) <- 1.0
rho
```

@@

```{r ch030-rvec10, eval = FALSE}
x <- bigsimr::rvec(10, rho = rho, margins = margins, type = "spearman")
```

```{r ch030-gpuWarn, echo=FALSE}
warning("warning.warn('No GPU/TPU found, falling back to CPU.')")
```

@@

```{r ch030-printX, eval = FALSE}
x
```

@@

```{r ch030-rvec1e6, fig.width=7, eval = FALSE}
x <- rvec(1e6, rho = rho, margins = margins, type = "spearman")

@@

```{r ch030-fastCor, eval = FALSE}
## help( package = 'bigsimr')
bigsimr::cor_fast(x, method = 'spearman')
```

@@

```{r ch030-computeBounds, echo = FALSE, eval=FALSE}
## Possibly bug? or configuration
## Error: segfault from C stack overflow on my Okapi bigsimr env 
rho_bounds <- bigsimr::computeCorBounds(margins = margins, type = 'spearman', cores = 1, reps = 1e5)
rho_bounds
```

@@

```{r ch030-rvecRslurm, echo=FALSE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)
```

```{r ch030-rvecRslurmRes, echo=FALSE, eval=FALSE}
res <- readRDS(file.path('_rslurm_rvec', list.files('_rslurm_rvec', 'results')))
head(res, 3)
## cleanup_files(sjob) ## careful this deletes output also
```

@@

```{r ch030-rvecRslurmMap, echo=FALSE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
set.seed(06202020)
simReps <- 100
rhoList <- replicate( n = simReps, bigsimr::rcor(d = length(margins), constant_rho = TRUE), simplify=FALSE )
sjob <- slurm_map(x = rhoList,
                  f = rvec,
                  jobname = 'rvecMap',
                  n=1e6,
                  margins = margins,
                  type = "spearman",
                  nodes = 4,
                  cpus_per_node = 4,
                  submit = TRUE)

@@

```{r ch030-rvecRslurmMapRes, echo=FALSE, eval=FALSE}
list.files('_rslurm_rvecMap', 'results')
res <- rslurm::get_slurm_out(sjob, outtype = 'raw')
rhoHats <- lapply( res, bigsimr::fastCor, method = 'spearman' )

@@

```{r ch030-rvecRslurmMapFig, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, out.width= '75%', fig.align='center', fig.cap='The continous marginal pairs exact reproduce the specified correlation whereas the discrete pairs (green nad blue) show a downward bias. Future work with employ a discrete adjusted procedures using *rescaling* on the traditional correlation coefficient.'}
library(tidyverse)

### 2020-10-21 040-monte-carlo-evaluation.Rmd
clean up auto genereated files

```{r LoadLib040, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
## devtools::install_github("SchisslerGroup/bigsimr", ref = 'develop')
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
## cores <- as.integer( 1 )
set.seed(10162020)
```

```{r previewChapter040, echo = FALSE, eval = FALSE}
bookdown::preview_chapter('040-monte-carlo-evaluation.Rmd')
```

@@

```{r biNormal, echo = FALSE, eval = TRUE}
mom_norm <- function(x) {
  m <- mean(x)
  s <- sd(x)
  list(mean = m, sd = s)
}

@@

```{r biNormPlot, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, fig.height = 5, fig.width= 8, fig.align='center', fig.cap = "`bigsimr` recovers the Pearson specified correlations for MVN."}
dat <- readRDS("./results/norm_sims.rds")
dat %>%
    filter(cores == cores) %>%
    ggplot(aes(rho, rho_hat, color = type)) +
    ## ggplot(aes(rho, rho_hat)) +
    geom_point() +
    geom_abline(slope = 1) +
    ## facet_wrap(~ + N) + theme_bw()
    facet_wrap(~ type + N) + theme_bw()

@@

```{r biGamma, echo = FALSE, eval = TRUE}
mom_gamma <- function(x) {
  m <- mean(x)
  s <- sd(x)
  list(shape = m^2 / s^2, rate = m / s^2)
}

@@

```{r biGammaPlot, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, fig.height = 5, fig.width= 8, fig.align='center', fig.cap = "`bigsimr` recovers the Pearson specified correlations for Bivariate Gamma."}
dat <- readRDS("./results/sims_gamma.rds")
dat %>%
    filter(cores == cores) %>%
    ggplot(aes(rho, rho_hat, color = type)) +
    ## ggplot(aes(rho, rho_hat)) +
    geom_point() +
    geom_abline(slope = 1) +
    ## facet_wrap(~ + N) + theme_bw()
    facet_wrap(~ type + N) + theme_bw()

@@

```{r biNegBin, echo = FALSE, eval = TRUE}
mom_nbinom <- function(x) {
  m <- mean(x)
  s <- sd(x)
  list(size = m^2 / (s^2 - m), prob = m / s^2)
}

@@

```{r  biNegBinPlot, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, fig.path='fig/plot-', dev='png', fig.ext='png', fig.align='center', fig.width = 8, fig.height=5,fig.cap = "`bigsimr` recovers the correlations for bivariate negative binomial only approximately for Pearson but (nearly) exactly for the rank-based correlations."}
dat <- readRDS("./results/nbinom_sims.rds")
dat %>%
    filter(cores == cores) %>%
    ggplot(aes(rho, rho_hat, color = type)) +
    ## ggplot(aes(rho, rho_hat)) +
    geom_point() +
    geom_abline(slope = 1) +
    ## facet_wrap(~ + N) + theme_bw()
    facet_wrap(~ type + N) + theme_bw()
## ggsave('fig/plot-biNegBinPlot.pdf')
```

@@

```{r gpuVScpuFig, echo=F, out.width='80%', fig.align='center', fig.cap="Computation times as d increases. We filter to the top 1, 5, 10, 15, 20, 25\\% expressing genes (in terms of median expression.)"}

knitr::include_graphics("fig/cpu-gpu-times.png")
```

>>>>

```{r ch040-LoadLib040, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
## devtools::install_github("SchisslerGroup/bigsimr", ref = 'develop')
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
## cores <- as.integer( 1 )
set.seed(10162020)
```

```{r ch040-preview, echo = FALSE, eval = FALSE}
bookdown::preview_chapter('040-monte-carlo-evaluation.Rmd')
```

@@

```{r ch040-biNormal, echo = FALSE, eval = TRUE}
mom_norm <- function(x) {
  m <- mean(x)
  s <- sd(x)
  list(mean = m, sd = s)
}

@@

```{r ch040-biNormPlot, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, fig.height = 5, fig.width= 8, fig.align='center', fig.cap = "`bigsimr` recovers the Pearson specified correlations for MVN."}
dat <- readRDS("./results/norm_sims.rds")
dat %>%
    filter(cores == cores) %>%
    ggplot(aes(rho, rho_hat, color = type)) +
    ## ggplot(aes(rho, rho_hat)) +
    geom_point() +
    geom_abline(slope = 1) +
    ## facet_wrap(~ + N) + theme_bw()
    facet_wrap(~ type + N) + theme_bw()

@@

```{r ch040-biGamma, echo = FALSE, eval = TRUE}
mom_gamma <- function(x) {
  m <- mean(x)
  s <- sd(x)
  list(shape = m^2 / s^2, rate = m / s^2)
}

@@

```{r ch040-biGammaPlot, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, fig.height = 5, fig.width= 8, fig.align='center', fig.cap = "`bigsimr` recovers the Pearson specified correlations for Bivariate Gamma."}
dat <- readRDS("./results/sims_gamma.rds")
dat %>%
    filter(cores == cores) %>%
    ggplot(aes(rho, rho_hat, color = type)) +
    ## ggplot(aes(rho, rho_hat)) +
    geom_point() +
    geom_abline(slope = 1) +
    ## facet_wrap(~ + N) + theme_bw()
    facet_wrap(~ type + N) + theme_bw()

@@

```{r ch040-biNegBin, echo = FALSE, eval = TRUE}
mom_nbinom <- function(x) {
  m <- mean(x)
  s <- sd(x)
  list(size = m^2 / (s^2 - m), prob = m / s^2)
}

@@

```{r ch040-biNegBinPlot, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, fig.path='fig/plot-', dev='png', fig.ext='png', fig.align='center', fig.width = 8, fig.height=5,fig.cap = "`bigsimr` recovers the correlations for bivariate negative binomial only approximately for Pearson but (nearly) exactly for the rank-based correlations."}
dat <- readRDS("./results/nbinom_sims.rds")
dat %>%
    filter(cores == cores) %>%
    ggplot(aes(rho, rho_hat, color = type)) +
    ## ggplot(aes(rho, rho_hat)) +
    geom_point() +
    geom_abline(slope = 1) +
    ## facet_wrap(~ + N) + theme_bw()
    facet_wrap(~ type + N) + theme_bw()
## ggsave('fig/plot-biNegBinPlot.pdf')
```

@@

```{r ch040-gpuVScpuFig, echo=F, out.width='80%', fig.align='center', fig.cap="Computation times as d increases. We filter to the top 1, 5, 10, 15, 20, 25\\% expressing genes (in terms of median expression.)"}
knitr::include_graphics("fig/cpu-gpu-times.png")
```

### 2020-10-21 050-examples.Rmd

```{r LoadLib050, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
set.seed(10142020)
```

```{r previewChapter050, echo = FALSE, eval = FALSE}
bookdown::preview_chapter('050-examples.Rmd')
```

@@

```{r readBRCA, echo=FALSE, eval=TRUE}
## full workflow simulating RNA-seq data
brca <- readRDS(file = 'data/brca99.rds') 
```

@@

```{r estRhoBRCA, echo=TRUE, eval=TRUE}
## 1. Estimate Spearman's correlation on the count data
## corType <- 'pearson'
corType <- 'spearman'
system.time( nb_Rho <- bigsimr::cor_fast( brca, method = corType ) )
```

```{r estMargins, echo = FALSE, eval = TRUE}
## 2. Estimate NegBin parameters using Method of Moments
estimateNegBinMoM <- function(tmpGene, minP = 1e-7) {
    tmpMean <- mean(tmpGene)
    tmpVar <- var(tmpGene)
    ## relate to nbinom parameters
    ## See ?rbinom for details.
    p <- tmpMean / tmpVar
    if (p < minP) {p <- minP } ## maybe add noise here
    n <- ( tmpMean * p) / ( 1  - p )  
    ## format for bigsimr margins
    return( list("nbinom", size = n, prob = p) )
}
brcaMargins <- apply( unname(as.matrix(brca)), 2, estimateNegBinMoM )
## describe the margins
probs <- unlist( lapply( brcaMargins, function(x) {x$prob} ) )
## summary(probs)
sizes <- unlist( lapply( brcaMargins, function(x) {x$size} ) )
## summary(sizes)
## head( sort( unlist( lapply( brcaMargins, function(x) {x$size} ) ) ) )
```

```{r nbHelpers}
make_nbinom_alist <- function(sizes, probs) {
  lapply(1:length(sizes), function(i) {
    substitute(qnbinom(size = s, prob = p), 
               list(s = sizes[i], p = probs[i]))
  })
}
## make_nbinom_alist(c(20, 21, 22), c(0.3, 0.4, 0.5))
nbinom_mom <- function(x) {
  m <- mean(x)
  s <- sd(x)
  s2 <- s^2
  p <- m/s2
  r <- m^2 / (s2 - m)
  c(r, p)
}
```

@@

```{r runBRCA, echo=TRUE, results=TRUE, cache = TRUE}
## Set the number of random vectors
n <- 10000
## construct margins
nb_margins <- make_nbinom_alist(sizes, probs)
## run sims
system.time( sim_nbinom <- rvec(n, nb_Rho, nb_margins, type = corType,
                                ensure_PSD = TRUE, cores = cores) )
colnames(sim_nbinom) <- names(brca)
```

@@

```{r simDataFig, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap='Simulated data for 3 randomly selected high-expressing genes, replicating the real data structure describing in the Introduction.'}
## retrieve the examples from an earlier chapter
## there is probably a better way to do this
exampleGenes <- readRDS(file = './data/exampleGenes.rds') 
GGally::ggpairs(data = as.data.frame(sim_nbinom[ ,exampleGenes] ))
```

@@

```{r figBRCA, echo=F, eval=T, fig.cap="bigsimr produces simulated random vectors from a multivariate negative binomial that replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters (vertical axes; derived from the simulated data) and the specified target parameters (horizontal axes)."}
par(mfrow=c(1,3))
## estimate rho from sims and plot
nb_Rho_hat <- cor_fast(sim_nbinom, method = corType)
plot(nb_Rho[lower.tri(nb_Rho)], nb_Rho_hat[lower.tri(nb_Rho_hat)],
     xlim = c(-1, 1), ylim = c(-1, 1),
     pch = 4, cex = 1, col = rgb(0, 0, 1, 0.05),
     xlab = "Target Correlation", ylab = "Estimated Correlation",
     main = "Correlation Matching")
abline(a = 0, b = 1, col="red", lty="dashed")
## estimate prob,size from sims and plot
nbinom_size_prob_hat <- apply(sim_nbinom, 2, nbinom_mom)
plot(sizes, nbinom_size_prob_hat[1,],
     pch = 4, cex = 1, col = rgb(0, 0, 1, 1),
     xlab = "Target Size", ylab = "Estimated Size",
     main = "Marginal NB Size Matching")
abline(a=0, b=1, col="red", lty="dashed")
plot(log(probs), log(nbinom_size_prob_hat[2,]),
     pch = 4, cex = 1, col = rgb(0, 0, 1, 1),
     xlab = "Target Log Probability", ylab = "Estimated Log Probability",
     main = "Marginal NB Probability Matching")
abline(a=0, b=1, col="red", lty="dashed")
par(mfrow=c(1,1))
```

@@

```{r densityEvaluation, echo=TRUE, eval=TRUE}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep( 1000, d)
mean(apply( sim_nbinom,  1,
           function(X, y0=threshold) {
               all( X > y0) }
           ))
```

@@

```{r corrTest, echo=FALSE, eval=FALSE, include=FALSE}

>>>>

```{r ch050-LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
set.seed(10142020)
```

```{r ch050-preview, echo = FALSE, eval = FALSE}
bookdown::preview_chapter('050-examples.Rmd')
```

@@

```{r ch050-readBRCA, echo=FALSE, eval=TRUE}
## full workflow simulating RNA-seq data
brca <- readRDS(file = 'data/brca99.rds') 
```

@@

```{r ch050-estRhoBRCA, echo=TRUE, eval=TRUE}
## 1. Estimate Spearman's correlation on the count data
## corType <- 'pearson'
corType <- 'spearman'
system.time( nb_Rho <- bigsimr::cor_fast( brca, method = corType ) )
```

```{r ch050-estMargins, echo = FALSE, eval = TRUE}
## 2. Estimate NegBin parameters using Method of Moments
estimateNegBinMoM <- function(tmpGene, minP = 1e-7) {
    tmpMean <- mean(tmpGene)
    tmpVar <- var(tmpGene)
    ## relate to nbinom parameters
    ## See ?rbinom for details.
    p <- tmpMean / tmpVar
    if (p < minP) {p <- minP } ## maybe add noise here
    n <- ( tmpMean * p) / ( 1  - p )  
    ## format for bigsimr margins
    return( list("nbinom", size = n, prob = p) )
}
brcaMargins <- apply( unname(as.matrix(brca)), 2, estimateNegBinMoM )
## describe the margins
probs <- unlist( lapply( brcaMargins, function(x) {x$prob} ) )
## summary(probs)
sizes <- unlist( lapply( brcaMargins, function(x) {x$size} ) )
## summary(sizes)
## head( sort( unlist( lapply( brcaMargins, function(x) {x$size} ) ) ) )
```

```{r ch050-nbHelpers}
make_nbinom_alist <- function(sizes, probs) {
  lapply(1:length(sizes), function(i) {
    substitute(qnbinom(size = s, prob = p), 
               list(s = sizes[i], p = probs[i]))
  })
}
## make_nbinom_alist(c(20, 21, 22), c(0.3, 0.4, 0.5))
nbinom_mom <- function(x) {
  m <- mean(x)
  s <- sd(x)
  s2 <- s^2
  p <- m/s2
  r <- m^2 / (s2 - m)
  c(r, p)
}
```

@@

```{r ch050-runBRCA, echo=TRUE, results=TRUE, cache = TRUE}
## Set the number of random vectors
n <- 10000
## construct margins
nb_margins <- make_nbinom_alist(sizes, probs)
## run sims
system.time( sim_nbinom <- rvec(n, nb_Rho, nb_margins, type = corType,
                                ensure_PSD = TRUE, cores = cores) )
colnames(sim_nbinom) <- names(brca)
```

@@

```{r ch050-simDataFig, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap='Simulated data for 3 randomly selected high-expressing genes, replicating the real data structure describing in the Introduction.'}
## retrieve the examples from an earlier chapter
## there is probably a better way to do this
exampleGenes <- readRDS(file = './data/exampleGenes.rds') 
GGally::ggpairs(data = as.data.frame(sim_nbinom[ ,exampleGenes] ))
```

@@

```{r ch050-figBRCA, echo=F, eval=T, fig.cap="bigsimr produces simulated random vectors from a multivariate negative binomial that replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters (vertical axes; derived from the simulated data) and the specified target parameters (horizontal axes)."}
par(mfrow=c(1,3))
## estimate rho from sims and plot
nb_Rho_hat <- cor_fast(sim_nbinom, method = corType)
plot(nb_Rho[lower.tri(nb_Rho)], nb_Rho_hat[lower.tri(nb_Rho_hat)],
     xlim = c(-1, 1), ylim = c(-1, 1),
     pch = 4, cex = 1, col = rgb(0, 0, 1, 0.05),
     xlab = "Target Correlation", ylab = "Estimated Correlation",
     main = "Correlation Matching")
abline(a = 0, b = 1, col="red", lty="dashed")
## estimate prob,size from sims and plot
nbinom_size_prob_hat <- apply(sim_nbinom, 2, nbinom_mom)
plot(sizes, nbinom_size_prob_hat[1,],
     pch = 4, cex = 1, col = rgb(0, 0, 1, 1),
     xlab = "Target Size", ylab = "Estimated Size",
     main = "Marginal NB Size Matching")
abline(a=0, b=1, col="red", lty="dashed")
plot(log(probs), log(nbinom_size_prob_hat[2,]),
     pch = 4, cex = 1, col = rgb(0, 0, 1, 1),
     xlab = "Target Log Probability", ylab = "Estimated Log Probability",
     main = "Marginal NB Probability Matching")
abline(a=0, b=1, col="red", lty="dashed")
par(mfrow=c(1,1))
```

@@

```{r ch050-densityEvaluation, echo=TRUE, eval=TRUE}
d <- ncol(sim_nbinom)
B <- nrow(sim_nbinom)
threshold <- rep( 1000, d)
mean(apply( sim_nbinom,  1,
           function(X, y0=threshold) {
               all( X > y0) }
           ))
```

@@

```{r ch050-corrTest, echo=FALSE, eval=FALSE, include=FALSE}
